---
title: "Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(molecularr)
```

why is it a good idea to limit the number of dependencies your package has. When can’t it always be avoided?:

1\. More stable Fewer external packages means fewer chances of breakage when upstream packages change or are removed.

2\. Faster to install Users (and CRAN) appreciate packages that install quickly without pulling in dozens of others.

3\. Easier to maintain You reduce the risk of version conflicts and simplify debugging when something goes wrong.

4\. More portable Lightweight packages are easier to use in constrained environments (e.g., servers, Docker containers, CI pipelines).

5\. CRAN-friendly CRAN reviewers often flag excessive dependencies, especially if they’re only used for minor tasks. can't avoid dependencies when:.....

1\. Core functionality If your package relies heavily on another (e.g., ggplot2 for plotting, dplyr for data wrangling), importing it is justified.

2\. Avoiding reinventing the wheel Rewriting well-tested functions (like str_split or geom_col) is inefficient and error-prone.

3\. Interoperability If your package is meant to work with others (e.g., extending tidymodels or Bioconductor tools), dependencies are expected.

4\. Performance or reliability Some packages offer optimized, battle-tested solutions that outperform custom code
